The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-03-26 SC-challenge.tex
some edits in sections 2 & 3

Multiple organizations, including the WSSSPE Software Credit~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Groups, are working to standardize software citation practices.
Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the FORCE11~\citeN{DataCitation2014} to standardize research data citation practices.
Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\cite{GitHubZenodo} to register DOIs for GitHub software releases.
The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).

@@

\katznote{Some ideas: \\
\url{https://softwaredatacitation.org/} \\
\url{http://www.software.ac.uk/software-credit}  \\
\url{http://astronomy-software-index.github.io/2015-workshop/} \\
\url{https://geodynamics.org/cig/projects/saga/} \\
maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}}
\knnote{Workshop reports} \cite{Sufi:2014en,Ahalt:2015ve}; Software Publishing Special Interest Group\cite{Allen:2015ub}

@@

The authors of this paper are currently leading a working group under FORCE11 to develop principles for software citation~\cite{SCWG}.
The draft principles document~\cite{SoftwareCitation2016}, which is adapted from an earlier set of principles for data citation~\cite{DataCitation2014}, discusses how to decide what software to cite:

>>>>

Multiple organizations, including the WSSSPE Software Credit working group~\cite{WSSSPE1,WSSSPE2,WSSSPE3} and FORCE11 Software Citation Working Group~\citeyear{SCWG}, are working to standardize software citation practices.
Some of the observations and recommendations made here come from their efforts, which follow similar work by DataCite and the FORCE11~\citeN{DataCitation2014} to standardize research data citation practices.
Currently, services including Zenodo or fig\textbf{share} allow software developers to obtain DOIs for software; the former has a streamlined process~\citeyear{GitHubZenodo} to register DOIs for GitHub software releases.
The CodeMeta project~\cite{CodeMeta} is formalizing minimal metadata schemas in JSON and XML to connect existing software repositories, archives, and libraries (e.g., GitHub, fig\textbf{share}, Zenodo).

@@

\katznote{Some ideas: \\
\url{https://softwaredatacitation.org/} \\
\url{http://www.software.ac.uk/software-credit}  \\
\url{http://astronomy-software-index.github.io/2015-workshop/} \\
\url{https://geodynamics.org/cig/projects/saga/} \\
maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}}
\knnote{Workshop reports} \cite{Sufi:2014en,Ahalt:2015ve}; Software Publishing Special Interest Group~\cite{Allen:2015ub}

@@

The authors of this paper are currently leading the FORCE11 Software Citation Working Group to develop principles for software citation~\citeyear{SCWG}.
The draft principles document~\cite{SoftwareCitation2016}, which is adapted from an earlier set of principles for data citation~\cite{DataCitation2014}, discusses how to decide what software to cite:
